Collaborative Visual Analysis on the Web with RCloud

### 2015-06-25 system.tex

The solution we developed is simple and general, and was directly
inspired by Miller's \emph{object
  capabilities}~\cite{Miller:2006:RCT}. Specifically, the R layer that
communicates with Javascript does not expose unprotected evaluation of
arbitrary functions. Instead, every function that the R layer intends
to expose is associated with a large, cryptographically-safe random
number (a ``hash''). This random number is then sent
across the wire. This number is interpreted as an opaque identifier to
a function. Because these identifiers are cryptographically safe, all
that the Javascript layer can do is return them to the R side, in a
message requesting that this function be called on its behalf. In that
case, the results of this function call might include \emph{new}
opaque identifiers, exposing new ``capabilities'' to the web browser.

>>>>

The solution we developed is simple and general, and was directly
inspired by Miller's \emph{object
  capabilities}~\cite{Miller:2006:RCT}. Specifically, the R layer that
communicates with Javascript does not expose unprotected evaluation of
arbitrary functions. Instead, every function that the R layer intends
to expose is associated with a large, cryptographically-safe random
number (a ``hash''). This random number is then sent
across the wire and interpreted as an opaque function identifier.
Because these identifiers are cryptographically safe, all
the Javascript layer can do is send them to the R side, in a
message requesting a function call. 
The result of this function call might include \emph{new}
opaque identifiers, exposing new ``capabilities'' to the client.
